Efficient Coalition Formation \\ for Web Services

### 2013-07-05 papers/coalition-journal-extension/coalition_journal.tex
Changes

As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda V(C)$ is devided among the community members. We have analysed the effect of subsiding and the cost it incurs to our web service communities. Figure \ref{f_taxtation} shows the results. In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration. Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases. However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly. Therefore subsiding can be costly for larger number of $\lambda$ value. Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration. It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration. The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community. These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.

>>>>

As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda v(C)$ is devided among the community members. We have analysed the effect of subsiding and the cost it incurs to our web service communities. Figure \ref{f_taxtation} shows the results. In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration. Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases. However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly. Therefore subsiding can be costly for larger number of $\lambda$ value. Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration. It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration. The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community. These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.
